---
title: "Statistical Learning of Water Spinodal"
author: "Folarin Latinwo"
date: "2/16/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Vapor-Liquid Spinodal

The spinodal represents the first stability limit for a substance in a given phase. Formally, this is defined by the condition, $$\left(\frac{\partial P}{\partial V}\right)_{T,s} \equiv 0.$$
where $P$ is the pressure, $V$ is the volume, $T$ is the temperature, and $s$ indicates the spinodal condition. The statement above necessary implies that the isothermal compressibility diverges at the spinodal. 

In this document, our goal is to analyze statistical models for the properties of the spinodal. Specifically, we will consider two models:

$$P_s=f(T)$$
$$A_s=\frac{\sqrt{8}}{3\sqrt{\left(\frac{\partial^2 P}{\partial^2 V}\right)_{T,s}}} = g(T)$$

Below, we consider a family of polynomial models for $f(T)$ and $g(T)$.

## f(T)
```{r fT}
data <- read.table('../src/Data/PTspinodal.txt',header=T)
attach(data)
lmA1=lm(pressure~poly(reduced_temperature,1))
lmA2=lm(pressure~poly(reduced_temperature,2))
lmA3=lm(pressure~poly(reduced_temperature,3))
lmA4=lm(pressure~poly(reduced_temperature,4))
anova(lmA1,lmA2)
anova(lmA2,lmA3)
anova(lmA3,lmA4)
plot(reduced_temperature,pressure)
lines(reduced_temperature,fitted(lmA3))
```

## g(T)

You can also embed plots, for example:

```{r gT}
rm(list=ls())
data <- read.table('../src/Data/ATspinodal.txt',header=T)
attach(data)
lmA1=lm(Afactor~poly(reduced_temperature,1))
lmA2=lm(Afactor~poly(reduced_temperature,2))
lmA3=lm(Afactor~poly(reduced_temperature,3))
lmA4=lm(Afactor~poly(reduced_temperature,4))
lmA5=lm(Afactor~poly(reduced_temperature,5))
anova(lmA1,lmA2)
anova(lmA2,lmA3)
anova(lmA3,lmA4)
anova(lmA4,lmA5)
plot(reduced_temperature,Afactor)
lines(reduced_temperature,fitted(lmA4))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
