---
title: "Unsupervised Learning of Liquid Polyamorphism"
author: "Folarin Latinwo"
date: "3/27/2017"
output: pdf_document
---

#TODO next: plot with respect to compressibility max and min. set origin at transition, and set axis at max (abs) slope

#TODO consider PCA with the same number of points

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #dplyr
library(FactoMineR) #MCA and PCA
```

Synopsis
---
Here, we will analyze the repsonse functions for systems that show liquid polyamorphism using techniques from machine learning. Specifically, the goal is to identify the essential (or generic) features that describe the properties of such systems using PCA and MCA. The models considered are the TIP4P2005, ST2, and Lattice Gas with chemical reaction.

## TIP4P2005 and ST2

Load the data
```{r}
TIP4P2005 <- read.table("../src/ScalingWaterModels/Features.dat",
                        header=T, stringsAsFactors = F) %>% as_tibble()
ST2 <- read.table("../src/ScalingWaterModels/FeaturesST2Widom.dat",
                        header=T, stringsAsFactors = F) %>% as_tibble()

TIP5P <- read.table("../src/ScalingWaterModels/FeaturesTIP5P.dat",
                        header=T, stringsAsFactors = F) %>% as_tibble()
```


What are the column names?
```{r}
names(TIP4P2005)
names(ST2)
names(TIP5P)<-c("Pressure","Temperature","Feature","Source")
#TIP5P$Source <- "MD"
```

What are the distinct Sources?
```{r}
TIP4P2005 %>% distinct(Feature)
TIP5P %>% distinct(Feature)
```

```{r}
TIP4P2005$Feature[TIP4P2005$Feature == "TminHighP"] <- "Tmin"
```

Combine both models
```{r}
TIP4P2005$Model <- "TIP4P2005"
ST2$Model <- "ST2"
TIP5P$Model <- "TIP5P"

# Filter strange points
TIP5Pn <- TIP5P %>% filter(Temperature < 300., Pressure > -125.)

spn <- function(x){ t = (x-253.5)/253.5; return(-284.38 + 628.41*t - 720.12*t*t) }
t<-seq(225,350)
stT<-data.frame(Temperature=t,Pressure=spn(t))
stT$Feature<-"Spinodal"
stT$Model<-"ST2"
stT$Source<-"TSEOS"
#eqnTIP5P

WaterModels <- rbind(TIP4P2005,ST2,TIP5Pn,stT)
```


### State of the Art

```{r include=FALSE}
library(latex2exp)
plot(TeX("A $\\c_p^{max} \\, \\c_p^{min} \\, \\kappa_T^{max} \\kappa_T^{min} \\llt \\vls \\T^{max}_{\\rho}  \\T^{min}_{\\rho} \\llw $ formula: $\\frac{2hc^2}{\\lambda^5} \\, 
               \\frac{1}{e^{\\frac{hc}{\\lambda k_B T}} - 1}$"), cex=2)
```


Let us take a look at the original data for TIP4P2005
```{r fig.width=10,fig.height=11}
library(ggplot2)
theme_set(theme_bw(base_size = 24))
WaterModels %>% filter(Source=="TSEOS"|Source=="Poole"|Source=="MD") %>%
  ggplot(mapping=aes(Temperature,Pressure,color=factor(Feature))) +
  geom_point(size=2) + 
  facet_grid(.~Model) +
  geom_point(data =subset(WaterModels,Feature=="LLCP"),
             aes(x = Temperature, y = Pressure), size = 8, shape=21,fill="white",
             show.legend=FALSE,stroke=3) +
  scale_color_discrete(name="",
                       labels=lapply(c("$\\c_p^{max}$",
                                       "$\\c_p^{min}$",
                                       "$\\kappa_T^{max}$",
                                       "$\\kappa_T^{min}$",
                                       "llcp","llt", "vls",
                                       "$\\T^{max}_{\\rho}$",
                                       "$\\T^{min}_{\\rho}$",
                                       "llw"),TeX)) +
  guides(col=guide_legend(nrow=5)) +
  theme(legend.position=c(0.05,0.85),
        aspect.ratio=1,legend.background=element_rect(fill=NA),
        strip.background = element_blank(),
       strip.text.x = element_blank())+
  xlim(150,400) + ylim(-500,475) +
  geom_text(data=data.frame(x=325,y=-400,Model=c("ST2","TIP4P2005","TIP5P")),
            aes(x,y,label=Model),inherit.aes = F,size=10) +
  xlab("Temperature (K)") + ylab("Pressure (MPa)")

ggsave("TIP4P2005ST2TIP5PFacetGridRaw.pdf")

#Next plot Widom-Line Spinodal
#Then P/Pc and T/Tc
#Then compressibility resaling

```



```{r fig.width=4, fig.height=4}
#Lattice Gas with Reaction Scaling
library(ggplot2)

LGRXNModels_1 <- read.table("../src/ScalingWaterModels/LGRXN-All.dat",header=T) %>% as_tibble()
LGRXNModels_2 <- read.table("../src/ScalingWaterModels/LGRXN-All-2.dat",header=T) %>% as_tibble()
LGRXNModels_3 <- read.table("../src/ScalingWaterModels/LGRXN-All-3.dat",header=T) %>% as_tibble()

LG <- rbind(LGRXNModels_2,LGRXNModels_1,LGRXNModels_3)
theme_set(theme_bw(base_size = 24))
LG %>% 
  ggplot() + geom_path(aes(Temperature,Pressure,color=Property),size=1.1) +
  facet_grid(~Source) +

  geom_point(data =subset(LG,Property=="LLCP"),
             aes(x = Temperature, y = Pressure), size = 3., shape=21,fill="white",
             show.legend=F,inherit.aes=F,stroke=1) +
  scale_color_discrete(name="", labels=lapply(c("$\\c_p^{ext.}$",
                                       "$\\kappa_T^{ext.}$","LLCP",
                                       "LLT", "WL","LVS",
                                       "$\\T^{ext.}_{\\rho}$"),TeX)) +
  guides(col=guide_legend(nrow=4),
         shape=guide_legend(ncol=1)) +
  theme(legend.position=c(0.11,0.825),legend.text=element_text(size=12),
        aspect.ratio=1,legend.background=element_rect(fill=NA),
        strip.background = element_blank(),
       strip.text.x = element_blank()) +
   scale_x_continuous(name=expression(italic("T")),breaks=c(0.0,0.5,1.0)) +
   ylab(expression(italic("P")))
ggsave("LatticeGasModelsRawSmaller.pdf")
```




# Interaction between Widom and Spinodal Line scaling
Now we consider the case for which the the driving force is the spinodal and the widom line. Do not distinguish between Tmin and TminHighP
```{r}
rWaterModels <- read.table("../src/ScalingWaterModels/Combined-07/All-1.dat",
                        header=T, stringsAsFactors = F) %>% as_tibble()
rWaterModels$Property[rWaterModels$Property == "TminHighP"] <- "Tmin"
rWaterModels$Property[rWaterModels$Property == "KtMax"] <- "Ktmax"
rWaterModels %>% distinct(Property)

```

Now display both models.
```{r fig.width=10,fig.height=11}
library(ggplot2)
myshapes<-rep(16,10)
myshapes[5]<-21
theme_set(theme_bw(base_size = 20))
rWaterModels %>% filter(Source=="TSEOS"|Source=="Poole") %>%
  ggplot(mapping=aes(Temperature,Pressure,color=factor(Property))) +
  geom_point(size=2) + 
  facet_grid(Model~.) +
  geom_point(data =subset(rWaterModels,Property=="LLCP"),
             aes(x = Temperature, y = Pressure), size = 8, shape=21,fill="white",
             show.legend=FALSE,stroke=3) +
  guides(col=guide_legend(nrow=5,override.aes = list(size=4,shape=myshapes))) +
  scale_color_discrete(name="", labels=lapply(c("$\\c_p^{max}$",
                                       "$\\c_p^{min}$",
                                       "$\\kappa_T^{max}$",
                                       "$\\kappa_T^{min}$",
                                       "llcp","llt", "vls",
                                       "$\\T^{max}_{\\rho}$",
                                       "$\\T^{min}_{\\rho}$",
                                       "llw"),TeX) ) +
  theme(legend.position=c(0.25,0.90),
        aspect.ratio=1,legend.background=element_rect(fill=NA),
        strip.background = element_blank(),
       strip.text.y = element_blank()) +
  xlab("Temperature (K)") + ylab("Pressure (MPa)") +
  geom_text(data=data.frame(x=-100,y=100,Model=c("ST2","TIP4P2005")),
            aes(x,y,label=Model),inherit.aes = F,size=8)
#ggsave("TIP4P2005ST2FacetGridRescaled.pdf")
```


```{r fig.width=6,fig.height=6}
library(ggplot2)
myshapes<-rep(16,10)
myshapes[5]<-21
theme_set(theme_bw(base_size = 30))
rWaterModels %>% filter(Source=="TSEOS"|Source=="Poole") %>%
  ggplot(mapping=aes(Temperature,Pressure,color=factor(Property),shape=Model)) +
  geom_point(size=3) +
  geom_point(data =subset(rWaterModels,Property=="LLCP"),
             aes(x = Temperature, y = Pressure), size = 8, shape=c(21,24),fill="white",
             show.legend=FALSE,stroke=3) +
  guides(col=guide_legend(nrow=5,override.aes = list(size=3,shape=myshapes)),
         shape=guide_legend(ncol=1)) +
  scale_color_discrete(name="", labels=lapply(c("$\\c_p^{max}$",
                                       "$\\c_p^{min}$",
                                       "$\\kappa_T^{max}$",
                                       "$\\kappa_T^{min}$",
                                       "llcp","llt", "vls",
                                       "$\\T^{max}_{\\rho}$",
                                       "$\\T^{min}_{\\rho}$",
                                       "llw"),TeX) ) +
  theme(legend.position=c(0.15,0.70),
        aspect.ratio=1,legend.background=element_rect(fill=NA),
        strip.background = element_blank(),
       strip.text.y = element_blank()) +
  xlab(TeX("$\\T-T_w\\,(K) $")) + ylab(TeX("$\\P-P_s\\,(MPa) $"))
ggsave("TIP4P2005ST2Rescaled.pdf")
```
# Classic approach to scaling

```{r}
rWaterModelsC <- read.table("../src/ScalingWaterModels/Combined-11/All-1.dat",
                        header=T, stringsAsFactors = F) %>% as_tibble()
rWaterModelsC$Property[rWaterModelsC$Property == "TminHighP"] <- "Tmin"
rWaterModelsC$Property[rWaterModelsC$Property == "KtMax"] <- "Ktmax"
rWaterModelsC %>% distinct(Property)

```

Now display both models.
```{r fig.width=10,fig.height=11}
library(ggplot2)
myshapes<-rep(16,10)
myshapes[5]<-21
theme_set(theme_bw(base_size = 20))
rWaterModelsC %>% filter(Source=="TSEOS"|Source=="Poole") %>%
  ggplot(mapping=aes(Temperature,Pressure,color=factor(Property))) +
  geom_point(size=2) + 
  facet_grid(Model~.) +
  geom_point(data =subset(rWaterModelsC,Property=="LLCP"),
             aes(x = Temperature, y = Pressure), size = 8, shape=21,fill="white",
             show.legend=FALSE,stroke=3) +
  guides(col=guide_legend(nrow=5,override.aes = list(size=4,shape=myshapes))) +
  scale_color_discrete(name="", labels=lapply(c("$\\c_p^{max}$",
                                       "$\\c_p^{min}$",
                                       "$\\kappa_T^{max}$",
                                       "$\\kappa_T^{min}$",
                                       "llcp","llt", "vls",
                                       "$\\T^{max}_{\\rho}$",
                                       "$\\T^{min}_{\\rho}$",
                                       "llw"),TeX) ) +
  theme(legend.position=c(0.75,0.90),
        aspect.ratio=1,legend.background=element_rect(fill=NA),
        strip.background = element_blank(),
       strip.text.y = element_blank()) +
  xlab("T/Tc") + ylab("P/Pc") +
  geom_text(data=data.frame(x=1.75,y=-2,Model=c("ST2","TIP4P2005")),
            aes(x,y,label=Model),inherit.aes = F,size=8)
ggsave("TIP4P2005ST2FacetGridClassic.pdf")
```

Property together
```{r fig.width=6,fig.height=6}
library(ggplot2)
myshapes<-rep(16,10)
myshapes[5]<-21
theme_set(theme_bw(base_size = 20))
rWaterModelsC %>% filter(Source=="TSEOS"|Source=="Poole") %>%
  ggplot(mapping=aes(Temperature,Pressure,color=factor(Property),shape=Model)) +
  geom_point(size=2) +
  geom_point(data =subset(rWaterModelsC,Property=="LLCP"),
             aes(x = Temperature, y = Pressure), size = 8, shape=c(21,24),fill="white",
             show.legend=FALSE,stroke=3) +
  guides(col=guide_legend(nrow=5,override.aes = list(size=3,shape=myshapes)),
         shape=guide_legend(ncol=1)) +
  scale_color_discrete(name="", labels=lapply(c("$\\c_p^{max}$",
                                       "$\\c_p^{min}$",
                                       "$\\kappa_T^{max}$",
                                       "$\\kappa_T^{min}$",
                                       "llcp","llt", "vls",
                                       "$\\T^{max}_{\\rho}$",
                                       "$\\T^{min}_{\\rho}$",
                                       "llw"),TeX) ) +
  theme(legend.position=c(0.85,0.70),
        aspect.ratio=1,legend.background=element_rect(fill=NA),
        strip.background = element_blank(),
       strip.text.y = element_blank()) +
  xlab(TeX("$\\T/T_c$")) + ylab(TeX("$\\P/P_c"))
ggsave("TIP4P2005ST2Classic.pdf")
```


# Classic approach to scaling

```{r}
rWaterModelsCW <- read.table("../src/ScalingWaterModels/Combined-12/All-1.dat",
                        header=T, stringsAsFactors = F) %>% as_tibble()
rWaterModelsCW$Property[rWaterModelsCW$Property == "TminHighP"] <- "Tmin"
rWaterModelsCW$Property[rWaterModelsCW$Property == "KtMax"] <- "Ktmax"
rWaterModelsCW %>% distinct(Property)

```


Now display both models.
```{r fig.width=10,fig.height=11}
library(ggplot2)
myshapes<-rep(16,10)
myshapes[5]<-21
theme_set(theme_bw(base_size = 20))
rWaterModelsCW %>% filter(Source=="TSEOS"|Source=="Poole") %>%
  ggplot(mapping=aes(Temperature,Pressure,color=factor(Property))) +
  geom_point(size=2) + 
  facet_grid(Model~.) +
  geom_point(data =subset(rWaterModelsCW,Property=="LLCP"),
             aes(x = Temperature, y = Pressure), size = 8, shape=21,fill="white",
             show.legend=FALSE,stroke=3) +
  guides(col=guide_legend(nrow=5,override.aes = list(size=4,shape=myshapes))) +
  scale_color_discrete(name="", labels=lapply(c("$\\c_p^{max}$",
                                       "$\\c_p^{min}$",
                                       "$\\kappa_T^{max}$",
                                       "$\\kappa_T^{min}$",
                                       "llcp","llt", "vls",
                                       "$\\T^{max}_{\\rho}$",
                                       "$\\T^{min}_{\\rho}$",
                                       "llw"),TeX) ) +
  theme(legend.position=c(0.25,0.90),
        aspect.ratio=1,legend.background=element_rect(fill=NA),
        strip.background = element_blank(),
       strip.text.y = element_blank()) +
  xlab(TeX("$\\T-T_w$")) + ylab(TeX("$\\P/P_c$")) +
  geom_text(data=data.frame(x=50,y=-2,Model=c("ST2","TIP4P2005")),
            aes(x,y,label=Model),inherit.aes = F,size=8)
ggsave("TIP4P2005ST2FacetGridClassicWidom.pdf")
```

Property together
```{r fig.width=6,fig.height=6}
library(ggplot2)
myshapes<-rep(16,10)
myshapes[5]<-21
theme_set(theme_bw(base_size = 20))
rWaterModelsCW %>% filter(Source=="TSEOS"|Source=="Poole") %>%
  ggplot(mapping=aes(Temperature,Pressure,color=factor(Property),shape=Model)) +
  geom_point(size=2) +
  geom_point(data =subset(rWaterModelsCW,Property=="LLCP"),
             aes(x = Temperature, y = Pressure), size = 8, shape=c(21,24),fill="white",
             show.legend=FALSE,stroke=3) +
  guides(col=guide_legend(nrow=5,override.aes = list(size=3,shape=myshapes)),
         shape=guide_legend(ncol=1)) +
  scale_color_discrete(name="", labels=lapply(c("$\\c_p^{max}$",
                                       "$\\c_p^{min}$",
                                       "$\\kappa_T^{max}$",
                                       "$\\kappa_T^{min}$",
                                       "llcp","llt", "vls",
                                       "$\\T^{max}_{\\rho}$",
                                       "$\\T^{min}_{\\rho}$",
                                       "llw"),TeX) ) +
  theme(legend.position=c(0.20,0.70),
        aspect.ratio=1,legend.background=element_rect(fill=NA),
        strip.background = element_blank(),
       strip.text.y = element_blank()) +
  xlab(TeX("$\\T-T_w$")) + ylab(TeX("$\\P/P_c"))
ggsave("TIP4P2005ST2ClassicWidom.pdf")
```


# Classic approach to scaling

```{r}
fn <- "../src/ScalingWaterModels/Combined-13/All-1.dat"
fn <- "../src/ScalingWaterModels/All.dat"
rWaterModelsCW <- read.table(fn,
                        header=T, stringsAsFactors = F) %>% as_tibble()
rWaterModelsCW$Property[rWaterModelsCW$Property == "TminHighP"] <- "Tmin"
rWaterModelsCW$Property[rWaterModelsCW$Property == "KtMax"] <- "Ktmax"
rWaterModelsCW %>% distinct(Source)
```

Now display both models.
```{r fig.width=10,fig.height=11}
library(ggplot2)
myshapes<-rep(16,10)
myshapes[5]<-21
theme_set(theme_bw(base_size = 20))
rWaterModelsCW %>% filter(Source=="TSEOS"|Source=="Poole"|Source=="LGRXN") %>%
  ggplot(mapping=aes(Temperature,Pressure,color=factor(Property))) +
  geom_point(size=2) + 
  facet_grid(~Model) +
  geom_point(data =subset(rWaterModelsCW,Property=="LLCP"),
             aes(x = Temperature, y = Pressure), size = 8, shape=21,fill="white",
             show.legend=FALSE,stroke=3) +
  guides(col=guide_legend(nrow=5,override.aes = list(size=4,shape=myshapes))) +
  scale_color_discrete(name="", labels=lapply(c("$\\c_p^{max}$",
                                       "$\\c_p^{min}$",
                                       "$\\kappa_T^{max}$",
                                       "$\\kappa_T^{min}$",
                                       "llcp","llt", "vls",
                                       "$\\T^{max}_{\\rho}$",
                                       "$\\T^{min}_{\\rho}$",
                                       "llw"),TeX) ) +
  theme(legend.position=c(0.25,0.90),
        aspect.ratio=1,legend.background=element_rect(fill=NA),
        strip.background = element_blank(),
       strip.text.y = element_blank()) +
  xlab(TeX("$\\T-T_w$")) + ylab(TeX("$\\P/P_c$"))# +
  #geom_text(data=data.frame(x=50,y=-2,Model=c("ST2","TIP4P2005")),
      #      aes(x,y,label=Model),inherit.aes = F,size=8)
#ggsave("TIP4P2005ST2FacetGridWidomNew.pdf")
```

Property together
```{r fig.width=3.5,fig.height=3.5}
library(ggplot2)
myshapes<-rep(16,7)
myshapes[5]<-21
theme_set(theme_bw(base_size = 20))

#+ geom_vline(xintercept = 0, size=1, linetype="dashed"

rT <- WaterModels %>% filter(Model=="TIP5P")  %>% mutate(Source="Madrid")
names(rT)<-c("Temperature","Pressure","Property","Source","Model")


rX<-rWaterModelsCW %>% filter(Property!="Spinodal",Property!="Widom",Property != "LLT" )
rX <- rX %>% filter(!(Property=="Tmin" & Temperature > 0.))
rW <- rX %>% filter(Property != "Widom")
rB<-rW#[seq(1, nrow(rW), 5), ] 
rB<-rbind(rW,rT)

maxp <- rWaterModelsCW %>% filter(Property=="LLT") %>% summarise(max(Pressure))

rB %>% filter((Source=="Madrid"|Source=="Poole")&Property!="Spinodal") %>%
  ggplot(mapping=aes(Temperature,Pressure,color=factor(Property),shape=Model,alpha=Model)) +
  geom_hline(yintercept = 0, size=1.1) + geom_segment(aes(x = 0, y = 0, xend = 0, yend = 1),size=0.75,linetype="dashed",color="black") +
  geom_segment(aes(x = 0, y = 1., xend = 0, yend = 1.25),size=1.5,color="black") +
  geom_path(aes(x = Temperature, y = Pressure,color=factor(Property)),data=rX %>% filter(Source=="LGRXN"),show.legend = FALSE) +
  geom_point(size=2) +  scale_alpha_discrete(range=c(1, 1)) +
  geom_point(data =subset(rWaterModelsCW,Property=="LLCP",Source!="LGRXN"),
             aes(x = Temperature, y = Pressure,shape=factor(Model)), size = 2.25, shape=c(21,24,NA,NA),fill="white",
             show.legend=FALSE,stroke=3) +
  guides(col=guide_legend(nrow=4,override.aes = list(size=3,shape=myshapes)),
         shape=guide_legend(nrow=2,override.aes=list(size=3,shape=c(16,17,NA,18),linetype=0 ))) +
  scale_color_discrete(name="", labels=lapply(c("$\\c_p^{max}$",
                                       "$\\c_p^{min}$",
                                       "$\\kappa_T^{max}$",
                                       "$\\kappa_T^{min}$",
                                       "LLCP",
                                       "$\\T^{max}_{\\rho}$",
                                       "$\\T^{min}_{\\rho}$"),TeX) ) +
  theme(legend.position=c(0.2,0.75),
        aspect.ratio=1,legend.background=element_rect(fill=NA),
        strip.background = element_blank(),
       strip.text.y = element_blank()) +
  xlab(TeX("$\\lambda \\frac{T - T_w}{T_c}$")) + ylab(TeX("$\\frac{P - P_s}{P_c - P_s}")) +scale_x_continuous(limits = c(-0.75, 0.75)) + scale_y_continuous(limits=c(0.,1.25),breaks=c(0.0,0.25,0.50,0.75,1.0,1.25))
#ggsave("TIP4P2005ST2WidomNew-5.pdf")
```



#Lattice Gas Full Model
Property together
```{r fig.width=3.5,fig.height=3.5}
library(ggplot2)


LGRXNModels_1 <- read.table("../src/ScalingWaterModels/LGRXN-r-1.dat",header=T) %>% as_tibble()
LGRXNModels_2 <- read.table("../src/ScalingWaterModels/LGRXN-r-2.dat",header=T) %>% as_tibble()
LGRXNModels_3 <- read.table("../src/ScalingWaterModels/LGRXN-r-3.dat",header=T) %>% as_tibble()

LGRXNModels_3$Model<-"Model_A"
LGRXNModels_2$Model<-"Model_B"
LGRXNModels_1$Model<-"Model_C"

LG <- rbind(LGRXNModels_2,LGRXNModels_1)#,LGRXNModels_3)
myshapes<-rep(16,7)
myshapes[5]<-21
theme_set(theme_bw(base_size = 20))

#+ geom_vline(xintercept = 0, size=1, linetype="dashed"

rT <- LG # %>% filter(Model=="TIP5P")  %>% mutate(Source="Madrid")
names(rT)<-c("Temperature","Pressure","Property","Source","Model")
 
rB<-rT

maxp <- rB %>% filter(Property=="LLT") %>% summarise(max(Pressure))

rB %>%
  ggplot(mapping=aes(Temperature,Pressure,color=factor(Property),linetype=Model)) +
  geom_hline(yintercept = 0, size=1.1) + geom_segment(aes(x = 0, y = 0, xend = 0, yend = 1),size=0.75,linetype="dashed",color="black") +
  geom_path(aes(x = Temperature, y = Pressure,color=factor(Property)),data=rB %>% filter(Property!="LLCP",Property!="LLW",Property!="LLT",Property!="LVS"),show.legend = TRUE,inherit.aes=T)  +  scale_alpha_discrete(range=c(1, 1)) +
  geom_segment(aes(x = 0, y = 1., xend = 0, yend = 1.25),size=1.5,color="black") +
  guides(col=guide_legend(nrow=2),
         shape=guide_legend(nrow=2,override.aes=list(size=3,shape=c(16,17,NA,18),linetype=0 ))) +
    geom_point(data =subset(rB,Property=="LLCP"),
             aes(x = Temperature, y = Pressure,shape=factor(Model)), size = 2.25, shape=c(21,22),fill="white",color="black",
             show.legend=FALSE,stroke=3) +
  scale_color_discrete(name="", labels=lapply(c("$\\c_p^{ext.}$",
                                       "$\\kappa_T^{ext.}$",
                                       "$\\T^{ext.}_{\\rho}$"),TeX) ) +
  theme(legend.position=c(0.2,0.75),
        aspect.ratio=1,legend.background=element_rect(fill=NA),
        strip.background = element_blank(),
       strip.text.y = element_blank()) +
  xlab(TeX("$\\lambda_1 \\frac{T - T_w}{T_c}$")) + ylab(TeX("$\\lambda_2 \\frac{P - P_s}{P_c - P_s}")) +scale_x_continuous(limits = c(-0.75, 0.75)) + scale_y_continuous(limits=c(0.,1.50),breaks=c(0.0,0.25,0.50,0.75,1.0,1.25))
ggsave("LatticeGasRescaled-2.pdf")
```




```{r}
Cv<-read.table("../src/Data/collatedCV",sep="\t",stringsAsFactors = F, header=T) %>% as_tibble()
Cv
```


```{r fig.width=3,fig.height=3}
Cv %>% filter(!(Density <= 1020)) %>% 
  ggplot(aes(x=Temperature,y=Cv,color=factor(Density))) +
  geom_point(size=1.5) + facet_wrap(~Density,ncol=3) +
  theme(plot.title = element_text(lineheight=.8, face="bold",size=12),
          strip.text.x = element_blank(),legend.margin = unit(0, "cm")) +
  scale_x_continuous(name="Temperature (K)",breaks=c(225,275,325)) + 
  scale_y_continuous(name=expression(paste(italic("c")[v], " (J/kg K)")),breaks=c(4000,8000,12000),limits = c(4000,12000))  +
  theme(legend.position="none",aspect.ratio=1) +
  geom_text(aes(x=295.,y=11000.,label=paste(Density/1000.,"g/cc")),inherit.aes =T,size=4) + scale_color_brewer(palette = "Set1")
ggsave("Cv-2.pdf")
```



Perform PCA on only data from TSEOS to avoid double counting. Also, drop Features. Consider the case where the units are scaled.
```{r}
PCA_T5 <- TIP4P2005 %>% filter(Source=="TSEOS") %>% 
  select(Temperature,Pressure) %>% 
  PCA(scale.unit=T,graph=F)
```


Visualize the components
```{r fig.width=6,fig.height=6}
PC1<- PCA_T5$ind$coord[,1]
PC2<- PCA_T5$ind$coord[,2]
PC3<- TIP4P2005 %>% select(Feature)
PCsT <- data.frame(cbind(PC1,PC2))
PCsT['Model'] <- "TIP4P2005"

library(ggplot2)
ggplot(PCsT,aes(PC1,PC2)) + geom_point(size=1) + 
xlab("Major Component") + 
ylab("Minor Component") +
ggtitle("Normalized PCA for TIP4P2005") 
#plot(PCA_T5,select="cos2 2",title="Normalized PCA for feature engineering")
#title(x="Major Component at 70%")
#ggsave("TIP4P2005NormalizedPCA.pdf")
```

## ST2
Load the data
```{r}
ST2 <- read.table("../src/ScalingWaterModels/FeaturesST2Widom.dat",
                        header=T, stringsAsFactors = F) %>% as_tibble()
```

What are the column names?
```{r}
names(ST2)
ST2[ST2$Feature=="Spinodal",]<-ST2[ST2$Feature=="Spinodal",] %>% mutate(Pressure = Pressure-50.)
```

What are the distinct Sources?
```{r}
ST2 %>% distinct(Source)
```

Perform PCA on all data including TSEOS. There is no double counting here. Also, drop Features. Consider the case where the units are scaled.
```{r}
PCA_S2 <- ST2 %>% 
  select(Temperature,Pressure) %>% 
  PCA(scale.unit=T,graph=F)
```


Visualize the components
```{r fig.width=6, fig.height=6}
PC1<- PCA_S2$ind$coord[,1]
PC2<- PCA_S2$ind$coord[,2]
PC3<- ST2 %>% select(Feature)
PCsS <- data.frame(cbind(PC1,PC2))
PCsS["Model"] <- "ST2"

library(ggplot2)
ggplot(PCsS,aes(PC1,PC2)) + geom_point(size=1) + 
xlab("Major Component") + 
ylab("Minor Component") +
ggtitle("Normalized PCA for ST2") 
ggsave("ST2NormalizedPCA.pdf")
#plot(PCA_S2,select="cos2 5")
```

### On both ST2 and TIP4P2005 simultaneously
```{r}
PCAll <- rbind(PCsS,PCsT)
library(ggplot2)
ggplot(PCAll,aes(PC1,PC2,color=Model)) + geom_point(size=1) + 
xlab("Major Component") + 
ylab("Minor Component") +
ggtitle("Normalized PCA for ST2 and TIP4P2005")

```



### On both ST2 and TIP4P2005 together

Perform PCA on all data including TSEOS. There is no double counting here. Also, drop Features. Consider the case where the units are scaled.
```{r}

ALL <- rbind(ST2 %>%
               select(Temperature, Pressure) %>%
               mutate_all(funs(1*.)),TIP4P2005 %>%
               filter(Source == "TSEOS") %>%
               select(Temperature, Pressure))

PCA_A <- ALL %>% 
  select(Temperature,Pressure) %>%
  PCA(scale.unit=T,graph=F)
```


Visualize the components
```{r}
PC1<- PCA_A$ind$coord[,1]
PC2<- PCA_A$ind$coord[,2]
PCs <- data.frame(cbind(PC1,PC2))

library(ggplot2)
ggplot(PCs,aes(PC1,PC2)) + geom_point(size=1) + 
xlab("Principal Component 1") + 
ylab("Principal Component 2")  +
coord_flip()

#plot(PCA_T5,select="cos2 5")
```

The spinodal represents the first stability limit for a substance in a given phase. Formally, this is defined by the condition, $$\left(\frac{\partial P}{\partial V}\right)_{T,s} \equiv 0.$$
where $P$ is the pressure, $V$ is the volume, $T$ is the temperature, and $s$ indicates the spinodal condition. The statement above necessary implies that the isothermal compressibility diverges at the spinodal. 

In this document, our goal is to analyze statistical models for the properties of the spinodal. Specifically, we will consider two models:

$$P_s=f(T)$$
$$A_s=\frac{\sqrt{8}}{3\sqrt{\left(\frac{\partial^2 P}{\partial^2 V}\right)_{T,s}}} = g(T)$$

Below, we consider a family of polynomial models for $f(T)$ and $g(T)$.

## f(T)
```{r fT}
rm(list=ls())
data <- read.table('../src/Data/PTspinodal.txt',header=T)
attach(data)
lmA1=lm(pressure~poly(reduced_temperature,1))
lmA2=lm(pressure~poly(reduced_temperature,2))
lmA3=lm(pressure~poly(reduced_temperature,3))
lmA4=lm(pressure~poly(reduced_temperature,4))
anova(lmA1,lmA2)
anova(lmA2,lmA3)
anova(lmA3,lmA4)
plot(reduced_temperature,pressure)
lines(reduced_temperature,fitted(lmA2))
```

## g(T)

You can also embed plots, for example:

```{r gT}
rm(list=ls())
data <- read.table('../src/Data/ATspinodal.txt',header=T)
data <- data[2:21,]
class(data)
attach(data)
lmA1=lm(Afactor~poly(reduced_temperature,1))
lmA2=lm(Afactor~poly(reduced_temperature,2))
lmA3=lm(Afactor~poly(reduced_temperature,3))
lmA4=lm(Afactor~poly(reduced_temperature,4))
lmA5=lm(Afactor~poly(reduced_temperature,5))
anova(lmA1,lmA2)
anova(lmA2,lmA3)
anova(lmA2,lmA4)
anova(lmA3,lmA4)
anova(lmA4,lmA5)
plot(reduced_temperature,Afactor)
lines(reduced_temperature,fitted(lmA2))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.







